Modern BTree\\ techniques

### 2020-01-10 btree/presentation.tex
Add suffix truncation

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{listings}
\usepackage{marvosym}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[export]{adjustbox}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{minted}
\usemintedstyle{tango}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes.misc, fit}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{verbatim}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usetikzlibrary{trees}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage{forloop}
\usepackage{csquotes}

@@

\newcommand\tikzmark[1]{%
  \tikz[overlay,remember picture] \coordinate (#1);}

@@

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}
\tikzset{btree-key/.style={minimum height=1cm, pattern=north west lines, draw}}
\tikzset{btree-pointer/.style={minimum height=1cm, draw}}
\tikzset{btree-hide/.style={draw opacity=0, line width=0, pattern=none}}
\tikzset{btree-empty/.style={btree-pointer, dashed}}
\tikzset{btree-leaf/.style={fill=greenGood}}
\tikzset{btree-branch/.style={fill=gray!20}}
\tikzset{btree-line/.style={line width=0.5pt}}
\tikzset{btree-path/.style={btree-pointer, minimum width=0.8cm, fill=red, opacity=0.5}}
\tikzset{>=latex}
\tikzset{btree-high-key/.style={btree-key, pattern=north west lines, pattern color=red, draw=red}}
\tikzset{btree-key-prefix/.style={btree-key, minimum height=0.2cm, fill=red, opacity=0.5}}
\tikzset{btree-key-compare/.style={btree-key, minimum height=0.6cm, fill=blue, opacity=0.5}}

@@

    \begin{overprint}[8cm]
    \end{overprint}
    \end{center}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{listings}
\usepackage{marvosym}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[export]{adjustbox}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{minted}
\usemintedstyle{tango}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes.misc, fit}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{verbatim}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usetikzlibrary{trees}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage{forloop}
\usepackage{csquotes}
\usetikzlibrary{tikzmark}

@@

%\newcommand\tikzmark[1]{%
  %\tikz[overlay,remember picture] \coordinate (#1);}

@@

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}
\tikzset{btree-key/.style={minimum height=1cm, pattern=north west lines, draw}}
\tikzset{btree-pointer/.style={minimum height=1cm, draw}}
\tikzset{btree-hide/.style={draw opacity=0, line width=0, pattern=none}}
\tikzset{btree-empty/.style={btree-pointer, dashed}}
\tikzset{btree-leaf/.style={fill=greenGood}}
\tikzset{btree-branch/.style={fill=gray!20}}
\tikzset{btree-line/.style={line width=0.5pt}}
\tikzset{btree-path/.style={btree-pointer, minimum width=0.8cm, fill=red, opacity=0.5}}
\tikzset{>=latex}
\tikzset{btree-high-key/.style={btree-key, pattern=north west lines, pattern color=red, draw=red}}
\tikzset{btree-key-prefix/.style={btree-key, minimum height=0.2cm, fill=red, opacity=0.5}}
\tikzset{btree-key-compare/.style={btree-key, minimum height=0.6cm, fill=blue, opacity=0.5}}
\tikzset{arrow-pointer/.style={
        single arrow,
        minimum height=1.5cm,
        inner sep=3pt,
        line width=1pt,
        draw,
        color=gray,
        single arrow tip angle=45,
        single arrow head extend=0.1cm
    }
}

@@

    \begin{overprint}[8cm]
        \onslide<1>
        \begin{tabular}{lll}
            & Johnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & Miller Ned & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Jack & 01-02-2019 \\
        \end{tabular}

        \onslide<2>
        \begin{tabular}{lll}
            & Johnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & \tikzmark{middle}Miller Ned & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Jack & 01-02-2019 \\
        \end{tabular}
        \begin{tikzpicture}[overlay, remember picture]
            \node[arrow-pointer, left=0.5cm of {pic cs:middle}, yshift=0.2cm] {};
        \end{tikzpicture}

        \onslide<3>
        \begin{tabular}{lll}
            & Johnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & \tikzmark{middle}\colorbox{BurntOrange}{Miller N}ed & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Jack & 01-02-2019 \\
        \end{tabular}
        \begin{tikzpicture}[overlay, remember picture]
            \node[arrow-pointer, left=0.5cm of {pic cs:middle}, yshift=0.2cm] {};
        \end{tikzpicture}

        \onslide<4>
        \begin{tabular}{lll}
            & \tikzmark{middle}\colorbox{BurntOrange}{J}ohnson David & 04-02-2019 \\
            & Miller Kevin & 01-02-2019 \\
            & Miller Ned & 02-03-2019 \\
            & Miller Steven & 03-04-2019 \\
            & Smith Jack & 01-02-2019 \\
        \end{tabular}
        \begin{tikzpicture}[overlay, remember picture]
            \node[arrow-pointer, left=0.5cm of {pic cs:middle}, yshift=0.2cm] {};
        \end{tikzpicture}

    \end{overprint}
    \end{center}
\end{frame}
\note{
    Not a normalized version, but whole column version is in PG12
}

    \begin{center}
    \textbf{Indirection vector}
    \vspace{1cm}

    \begin{overprint}[8cm]
    \end{overprint}
